A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-01 02_Materials_and_Methods.Rmd
tightlist issue: https://tex.stackexchange.com/questions/257418/error-tightlist-converting-md-file-into-pdf-using-pandoc

1. Downloading the Radon-B dataset with the R package c14bazAAR [@schmidC14bazAARDownloadPrepare2018], which allows to access several open radiocarbon archives. (11048 dates)
2. Removing all dates without age information or age information outside of the limits of the Intcal13 calibration curve: 71 - 46401 BP [@reimer_intcal13_2013]. (10956 dates)
3. Calibrating the ^14^C dates with the R package Bchron [@haslettSimpleMonotoneProcess2008], which implements the calibration algorithm with numerical integration.
4. Reducing date selection to all dates whose $2\sigma$ calibrated age range overlap by at least one year with the predefined window of interest: 2200 -- 800 calBC. (7543 dates)
5. Reducing the date selection to all dates taken from graves as indicated by the *Feature type* variable. (2361)
6. Transforming the variable *Feature type* via pattern matching to two new variables *burial type* (inhumation/cremation/unknown) and *burial construction* (mound/flat/unknown).
7. Manually defining a rectangular (EPSG:102013) research area with sufficient information in Central-, Northern and Northwestern Europe based on perceived spatial date distribution (Figure **TODO**).
8. Reducing date selection to dates within the research area. (1894 dates)
9. Removing ^14^C date doubles with tools of c14bazAAR. (1848 dates)
10. Transforming data from the meaning *^14^C dates on graves* to *burial type at a certain time*. This is a more complex process, because **TODO** (1704 graves)
11. Defining macroregions. **TODO**
12. Reducing the date selection to the space covered by the macroregions and attributing the dates to the respective units. (1562 graves)

@@

- $d_{ij}^2$: SED between tqo groups $i$ and $j$
- $k$: trait counter 
- $n$: number of traits in the population
- $p_{ik}$: relative frequency of the $k$th trait in group $i$
- $p_{jk}$: relative frequency of the $k$th trait in group $j$

>>>>

1. Downloading the Radon-B dataset with the R package c14bazAAR [@schmidC14bazAARDownloadPrepare2018], which allows to access several open radiocarbon archives. (11048 dates)

2. Removing all dates without age information or age information outside of the limits of the Intcal13 calibration curve: 71 - 46401 BP [@reimer_intcal13_2013]. (10956 dates)

3. Calibrating the ^14^C dates with the R package Bchron [@haslettSimpleMonotoneProcess2008], which implements the calibration algorithm with numerical integration.

4. Reducing date selection to all dates whose $2\sigma$ calibrated age range overlap by at least one year with the predefined window of interest: 2200 -- 800 calBC. (7543 dates)

5. Reducing the date selection to all dates taken from graves as indicated by the *Feature type* variable. (2361)

6. Transforming the variable *Feature type* via pattern matching to two new variables *burial type* (inhumation/cremation/unknown) and *burial construction* (mound/flat/unknown).

7. Manually defining a rectangular (EPSG:102013) research area with sufficient information in Central-, Northern and Northwestern Europe based on perceived spatial date distribution (Figure **TODO**).

8. Reducing date selection to dates within the research area. (1894 dates)

9. Removing ^14^C date doubles with tools of c14bazAAR. (1848 dates)

10. Transforming data from the meaning *^14^C dates on graves* to *burial type at a certain time*. This is a more complex process, because **TODO** (1704 graves)

11. Defining macroregions. **TODO**

12. Reducing the date selection to the space covered by the macroregions and attributing the dates to the respective units. (1562 graves)

@@

- $d_{ij}^2$: SED between tqo groups $i$ and $j$

- $k$: trait counter

- $n$: number of traits in the population

- $p_{ik}$: relative frequency of the $k$th trait in group $i$

- $p_{jk}$: relative frequency of the $k$th trait in group $j$
